IRTF Spectro-Photometry of Rotating Brown Dwarfs

### 2016-10-25 ms.tex
I added a dynamic spectrum image. But it's got the wrong reference and background star order.
I added the amplitude versus wavelength plot for 2MASS J1821.

\section{Light Curves}
\begin{figure}[!ht]
\centering
\includegraphics[width=0.5\textwidth]{2mass_1821_t_series.pdf}
\caption{Time Series.}\label{fig:DHSRes}
\end{figure}

>>>>

\section{Light Curves}
\begin{figure}[!ht]
\centering
\includegraphics[width=0.5\textwidth]{specphot_j1821.pdf}
\caption{Top Panel: 2MASS 1821's median spectrum compared with the reference star. The reference star is a significantly higher temperature star. Bottom Panel: Dynamic spectrum of 2MASS J1821.}\label{fig:DHSRes}
\end{figure}

\begin{figure}[!ht]
\centering
\includegraphics[width=0.5\textwidth]{2mass_1821_t_series.pdf}
\caption{Time Series.}\label{fig:1821tser}
\end{figure}

\section{Light Curves}
\begin{figure}[!ht]
\centering
\includegraphics[width=0.5\textwidth]{amp_vs_wavl_j1821.pdf}
\caption{Sine fit amplitude versus wavelength for 2MASS J1821. The regions at 1.4~$\mu$m and 1.9~$\mu$m are contaminated by telluric absorption so the variations can likely be due to telluric variability not corrected by the reference star.}\label{fig:DHSRes}
\end{figure}
